---
title: "4_Results"
author: "massaine"
date: "2022-11-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

### Function Confusion matrix
```{r}
prettyConfused<-function(Actual,Predict,colors=c("white","red4",
                                     "dodgerblue3"),text.scl=5){
  actual = as.data.frame(table(Actual))
  names(actual) = c("Actual","ActualFreq")
  #build confusion matrix
  confusion = as.data.frame(table(Actual, Predict))
  names(confusion) = c("Actual","Predicted","Freq")
  #calculate percentage of test cases based on actual frequency
  confusion = merge(confusion, actual, by=c('Actual','Actual'))
  confusion$Percent = confusion$Freq/confusion$ActualFreq*100
  confusion$ColorScale<-confusion$Percent*-1
  confusion[which(confusion$Actual==confusion$Predicted),]$ColorScale<-confusion[which(confusion$Actual==confusion$Predicted),]$ColorScale*-1
  confusion$Label<-paste(round(confusion$Percent,0),"%, n=",
                         confusion$Freq,sep="")
  tile <- ggplot() + theme(panel.grid.major = element_blank(),
                           panel.grid.minor = element_blank(),
                          panel.background = element_blank(), 
                          axis.line = element_blank(),
                          axis.title.x = element_text(size = rel(1)),
                          axis.title.y = element_text(size = rel(1)),
                          axis.text.x = element_text(size=13),
                          axis.text.y = element_text(size=13)) +
              geom_tile(aes(x=Actual, y=Predicted,fill=ColorScale),
              data=confusion, color="black",size=0.1) +
              labs(x="Reference",y="Predicted")
  
  tile = tile + geom_text(aes(x=Actual,y=Predicted, label=Label),
              data=confusion, size=text.scl, colour="black") +
               scale_fill_gradient2(low=colors[2],
               high=colors[3],
               mid=colors[1],midpoint = 0,guide='none')
}
library(caret)
```

### Load results from classification models (SCIO)
```{r,eval=F}
resCV_1 <- list()
modelname <- c("KNN","CDT","xgbLinear","parRF")
ResCM <- matrix(NA,ncol=6,nrow = 16)

load(file=here::here("output","knn_SCIO_Model.RData"))
resCV_1[[1]] <- modelFit[[1]]
ResCM[1,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[1,3:4] <- CM[[1]]$byClass[c(1,2)]

load(file=here::here("output","C5.0_SCIO_Model.RData"))
resCV_1[[2]] <- modelFit[[1]]
ResCM[2,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[2,3:4] <- CM[[1]]$byClass[c(1,2)]

load(file=here::here("output","xgbLinear_SCIO_Model.RData"))
resCV_1[[3]] <- modelFit[[1]]
ResCM[3,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[3,3:4] <- CM[[1]]$byClass[c(1,2)]

load(file=here::here("output","parRF_SCIO_Model.RData"))
resCV_1[[4]] <- modelFit[[1]]
ResCM[4,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[4,3:4] <- CM[[1]]$byClass[c(1,2)]

res <- resamples(resCV_1)
res <- res$values
resCV_2 <- list()

for(i in 1:4){ 
  resCV_2[[i]]<-res[,c(paste(paste("Model",i,sep=""),"~Accuracy",sep=""), 
                       paste(paste("Model",i,sep=""),"~Kappa",sep=""))]
  resCV_2[[i]]$Model <- modelname[i]
  colnames(resCV_2[[i]]) <- c("Accuracy","Kappa","Model")}

Results_CV_S <- do.call(rbind,resCV_2)
Results_CV_S$NIR <- "SCiO"
```

### Load results from classification models (BUCHI)
```{r,eval=F}
resCV_1 <- list()

load(file=here::here("output","knn_BUCHI_Model.RData"))
resCV_1[[1]] <- modelFit[[1]]
ResCM[9,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[9,3:4] <- CM[[1]]$byClass[c(1,2)]

load(file=here::here("output","C5.0_BUCHI_Model.RData"))
resCV_1[[2]] <- modelFit[[1]]
ResCM[10,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[10,3:4] <- CM[[1]]$byClass[c(1,2)]

load(file=here::here("output","xgbLinear_BUCHI_Model.RData"))
resCV_1[[3]] <- modelFit[[1]]
ResCM[11,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[11,3:4] <- CM[[1]]$byClass[c(1,2)]

load(file=here::here("output","parRF_BUCHI_Model.RData"))
resCV_1[[4]] <- modelFit[[1]]
ResCM[12,1:2] <- CM[[1]]$overall[c(1,2)]
ResCM[12,3:4] <- CM[[1]]$byClass[c(1,2)]

res <- resamples(resCV_1)
res <- res$values
resCV_2 <- list()

for(i in 1:4){ 
  resCV_2[[i]]<-res[,c(paste(paste("Model",i,sep=""),"~Accuracy",sep=""), 
                       paste(paste("Model",i,sep=""),"~Kappa",sep=""))]
  resCV_2[[i]]$Model <- modelname[i]
  colnames(resCV_2[[i]]) <- c("Accuracy","Kappa","Model")}

Results_CV_B <- do.call(rbind,resCV_2)
Results_CV_B$NIR <- "BUCHI"
```

```{r,eval=FALSE}
#save(Results_CV_S,Results_CV_B,file = here::here("output","Results_CrossVal.RData"))
```

### BOXPlot Cross_validation (all variables)
```{r}
load(file = here::here("output","Results_CrossVal.RData"))

Results_CV_B$Model <- as.factor(Results_CV_B$Model)
Results_CV_S$Model <- as.factor(Results_CV_S$Model)
levels(Results_CV_B$Model) <- c("CDT","KNN", "RF","XGBL")
levels(Results_CV_S$Model) <- c("CDT","KNN", "RF","XGBL")

p1<-ggplot(Results_CV_S, aes(x=Model, y=Accuracy, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0.7, 1) + 
  ggtitle("B) SCiO") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))

p2<-ggplot(Results_CV_S, aes(x=Model, y=Kappa, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0, 1) +
  ggtitle("D) SCiO") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))
  
p3<-ggplot(Results_CV_B, aes(x=Model, y=Accuracy, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0.7, 1) +
  ggtitle("A) NIRFlex N-500") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))

p4<-ggplot(Results_CV_B, aes(x=Model, y=Kappa, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0, 1) +
  ggtitle("C) NIRFlex N-500") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))
 
library(ggpubr)
ggarrange(p3,p1,p4,p2,ncol=2,nrow=2)
```

### save plot Figure 2
```{r}
tiff(file = "Figure_1_CV_Allvariables.tiff", 
               width = 16, height=14, res = 700, 
               compression = "lzw", units = "cm")
ggarrange(p3,p1,p4,p2,ncol=2,nrow=2)
dev.off()
```

### Modelos with sel de espectros (scio)
```{r,eval=FALSE}
load(file = here::here("output","SCIO_Model_Sel_Var.RData"))
load(file = here::here("output","SCIO_testing_set.RData"))

modelname <- c("KNN","CDT","xgbLinear","parRF")

modelPredict <- predict(modelFitSEL_S1,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[5,1:2] <- CM$overall[c(1,2)]
    ResCM[5,3:4] <- CM$byClass[c(1,2)]
modelPredict <- predict(modelFitSEL_S2,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[6,1:2] <- CM$overall[c(1,2)]
    ResCM[6,3:4] <- CM$byClass[c(1,2)]
modelPredict <- predict(modelFitSEL_S3,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[7,1:2] <- CM$overall[c(1,2)]
    ResCM[7,3:4] <- CM$byClass[c(1,2)]
modelPredict <- predict(modelFitSEL_S4,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[8,1:2] <- CM$overall[c(1,2)]
    ResCM[8,3:4] <- CM$byClass[c(1,2)]

res <- resamples(list(Model1 = modelFitSEL_S1, Model2 = modelFitSEL_S2,
                      Model3 = modelFitSEL_S3, Model4 = modelFitSEL_S4))

res <- res$values
resCV_1 <- list()

for(i in 1:4){ 
  resCV_1[[i]]<-res[,c(paste(paste("Model",i,sep=""),"~Accuracy",sep=""), 
                       paste(paste("Model",i,sep=""),"~Kappa",sep=""))]
  resCV_1[[i]]$Model <- modelname[i]
  colnames(resCV_1[[i]]) <- c("Accuracy","Kappa","Model")}
  Results_CV_SEL_S <- do.call(rbind,resCV_1)
  Results_CV_SEL_S$NIR <- "SCIO"

  
```

### Modelos with sel de espectros (BUCHI)
```{r,eval=FALSE}
load(file = here::here("output","BUCHI_Model_Sel_Var.RData"))
load(file = here::here("output","BUCHI_testing_set.RData"))
modelname <- c("KNN","CDT","xgbLinear","parRF")

modelPredict <- predict(modelFitSEL_S1,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[13,1:2] <- CM$overall[c(1,2)]
    ResCM[13,3:4] <- CM$byClass[c(1,2)]
modelPredict <- predict(modelFitSEL_S2,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[14,1:2] <- CM$overall[c(1,2)]
    ResCM[14,3:4] <- CM$byClass[c(1,2)]
modelPredict <- predict(modelFitSEL_S3,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[15,1:2] <- CM$overall[c(1,2)]
    ResCM[15,3:4] <- CM$byClass[c(1,2)]
modelPredict <- predict(modelFitSEL_S4,newdata = testing[[1]])
    CM <- confusionMatrix(modelPredict, testing[[1]]$Waxy)
    ResCM[16,1:2] <- CM$overall[c(1,2)]
    ResCM[16,3:4] <- CM$byClass[c(1,2)]


res <- resamples(list(Model1 = modelFitSEL_S1, Model2 = modelFitSEL_S2,
                      Model3 = modelFitSEL_S3, Model4 = modelFitSEL_S4))

res <- res$values
resCV_1 <- list()

for(i in 1:4){ 
  resCV_1[[i]]<-res[,c(paste(paste("Model",i,sep=""),"~Accuracy",sep=""), 
                       paste(paste("Model",i,sep=""),"~Kappa",sep=""))]
  resCV_1[[i]]$Model <- modelname[i]
  colnames(resCV_1[[i]]) <- c("Accuracy","Kappa","Model")}
  Results_CV_SEL_B <- do.call(rbind,resCV_1)
  Results_CV_SEL_B$NIR <- "BUCHI"

#save(Results_CV_SEL_S,Results_CV_SEL_B,
#  file = here::here("output","Results_CrossVal_SEL.RData"))
```

### PLOT Confusion matrix parametros
```{r}
ResCM  
colnames(ResCM) <- c("acc","kappa","Sensitivity","Specificity","Model","NIR")
ResCM <- as.data.frame(ResCM)
ResCM[,5] <- modelname
ResCM$acc <- round(as.numeric(ResCM$acc),2)
ResCM$kappa <- round(as.numeric(ResCM$kappa),2)
ResCM$Sensitivity <- round(as.numeric(ResCM$Sensitivity),2)
ResCM$Specificity <- round(as.numeric(ResCM$Specificity),2)
ResCM$NIR <- rep(c("SCIO","SCIO_SEL","BUCHI","BUCHI_SEL"),each=4)
ResCM %>% gt()
```


### BOXPlot Cross_validation (variables SELECTED)
```{r}
load(file = here::here("output","Results_CrossVal_SEL.RData"))
Results_CV_SEL_S$Model <- as.factor(Results_CV_SEL_S$Model)
levels(Results_CV_SEL_S$Model) <- c("CDT_Sel","KNN_Sel",
                                    "RF_Sel","XGBL_Sel")

Results_CV_SEL_B$Model <- as.factor(Results_CV_SEL_B$Model)
levels(Results_CV_SEL_B$Model) <- c("CDT_Sel","KNN_Sel",
                                    "RF_Sel","XGBL_Sel")


p1<-ggplot(Results_CV_SEL_S, aes(x=Model, y=Accuracy, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0.7, 1) + 
  ggtitle("B) SCiO") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))

p2<-ggplot(Results_CV_SEL_S, aes(x=Model, y=Kappa, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0, 1) +
  ggtitle("D) SCiO") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))
  
p3<-ggplot(Results_CV_SEL_B, aes(x=Model, y=Accuracy, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0.7, 1) +
  ggtitle("A) NIRFlex N-500") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))

p4<-ggplot(Results_CV_SEL_B, aes(x=Model, y=Kappa, fill=Model)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() + ylim(0, 1) +
  ggtitle("C) NIRFlex N-500") +
  theme(legend.position = "none", legend.title =element_blank())+
  scale_fill_manual(values = c("#999999","orange","#56B4E9","olivedrab3"))
 
ggarrange(p3,p1,p4,p2,ncol=2,nrow=2)

```

### save plot Figure 4
```{r}
tiff(file = "Figure3_CV_SelVariables.tiff", 
               width = 16, height=14, res = 700, 
               compression = "lzw", units = "cm")
ggarrange(p3,p1,p4,p2,ncol=2,nrow=2)
dev.off()
```

### Table All variables BUCHI
```{r}
library(dplyr)
library(gt)

Res <- rbind(Results_CV_B,Results_CV_S,Results_CV_SEL_B,Results_CV_SEL_S)

Res%>%group_by(NIR,Model)%>%
   summarise(Acc = round(mean(Accuracy, na.rm = T),3),
             Kap = round(mean(Kappa, na.rm = T),3)) %>%
       gt()  %>%     tab_options(table.font.size = pct(75))
```


### Preparar resultados da matriz de confusao (SCIO)
```{r,eval=F}
load(file=here::here("output","SCIO_testing_set.RData"))
load(file=here::here("output","knn_SCIO_Model.RData"))
M1pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M1pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M1pred1 <- prettyConfused(testing[[1]]$Waxy,M1pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="KNN")

load(file=here::here("output","C5.0_SCIO_Model.RData"))
M2pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M2pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M2pred1 <- prettyConfused(testing[[1]]$Waxy,M2pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="CDT")


load(file=here::here("output","xgbLinear_SCIO_Model.RData"))
M3pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M3pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M3pred1 <- prettyConfused(testing[[1]]$Waxy,M3pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="XGB")


load(file=here::here("output","parRF_SCIO_Model.RData"))
M4pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M4pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M4pred1 <- prettyConfused(testing[[1]]$Waxy,M4pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="RF")
 
ggarrange(M1pred1,M2pred1,M3pred1,M4pred1,ncol=1,nrow=4)

```




### Preparar resultados da matriz de confusao (BUCHI)
```{r,eval=F}
load(file=here::here("output","BUCHI_testing_set.RData"))
load(file=here::here("output","knn_BUCHI_Model.RData"))
M5pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M5pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M5pred1 <- prettyConfused(testing[[1]]$Waxy,M5pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="KNN")

load(file=here::here("output","C5.0_BUCHI_Model.RData"))
M6pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M6pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M6pred1 <- prettyConfused(testing[[1]]$Waxy,M6pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="CDT")


load(file=here::here("output","xgbLinear_BUCHI_Model.RData"))
M7pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M7pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M7pred1 <- prettyConfused(testing[[1]]$Waxy,M7pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="XGB")


load(file=here::here("output","parRF_BUCHI_Model.RData"))
M8pred <- predict(modelFit[[1]],newdata = testing[[1]])
levels(M8pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M8pred1 <- prettyConfused(testing[[1]]$Waxy,M8pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="RF")
library(ggpubr) 
ggarrange(M5pred1,M6pred1,M7pred1,M8pred1,ncol=1,nrow=4)

```


### Preparar resultados da matriz de confusao (SCIO) Variable Selected
```{r,eval=F}
load(file=here::here("output","SCIO_testing_set.RData"))
load(file=here::here("output","SCIO_Model_Sel_Var.RData"))
M1pred <- predict(modelFitSEL_S1,newdata = testing[[1]])
levels(M1pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M1pred1s <- prettyConfused(testing[[1]]$Waxy,M1pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="KNN_Sel")

M2pred <- predict(modelFitSEL_S2,newdata = testing[[1]])
levels(M2pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M2pred1s <- prettyConfused(testing[[1]]$Waxy,M2pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="CDT_Sel")

M3pred <- predict(modelFitSEL_S3,newdata = testing[[1]])
levels(M3pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M3pred1s <- prettyConfused(testing[[1]]$Waxy,M3pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="XGB_Sel")

M4pred <- predict(modelFitSEL_S4,newdata = testing[[1]])
levels(M4pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M4pred1s <- prettyConfused(testing[[1]]$Waxy,M4pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="RF_Sel")
 
ggarrange(M1pred1s,M2pred1s,M3pred1s,M4pred1s,ncol=1,nrow=4)

```


### Preparar resultados da matriz de confusao (BUCHI) Variable Selected
```{r,eval=F}
load(file=here::here("output","BUCHI_testing_set.RData"))
load(file=here::here("output","BUCHI_Model_Sel_Var.RData"))
M5pred <- predict(modelFitSEL_S1,newdata = testing[[1]])
levels(M5pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M5pred1s <- prettyConfused(testing[[1]]$Waxy,M5pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="KNN_Sel")

M6pred <- predict(modelFitSEL_S2,newdata = testing[[1]])
levels(M6pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M6pred1s <- prettyConfused(testing[[1]]$Waxy,M6pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="CDT_Sel")

M7pred <- predict(modelFitSEL_S3,newdata = testing[[1]])
levels(M7pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M7pred1s <- prettyConfused(testing[[1]]$Waxy,M7pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="XGB_Sel")

M8pred <- predict(modelFitSEL_S4,newdata = testing[[1]])
levels(M8pred) <- c("Nonwaxy","Waxy")
levels(testing[[1]]$Waxy) <- c("Nonwaxy","Waxy")
M8pred1s <- prettyConfused(testing[[1]]$Waxy,M8pred,
                          colors=c("white","red4","dodgerblue3"),
                          text.scl = 5)+labs(title="RF_Sel")
library(ggpubr) 
ggarrange(M5pred1s,M6pred1s,M7pred1s,M8pred1s,ncol=1,nrow=4)

```

### Save and load Confusion Matrix plot
```{r,eval=FALSE}
save(M1pred1,M2pred1,M3pred1,M4pred1,M5pred1,M6pred1,M7pred1,M8pred1,
     M1pred1s,M2pred1s,M3pred1s,M4pred1s,M5pred1s,M6pred1s,M7pred1s,
     M8pred1s, file = here::here("output","Plot_ConfMatrix.RData"))
```

### Plot
```{r}
load( file = here::here("output","Plot_ConfMatrix.RData"))

library(ggpubr) 

tiff(file = "Figure5_MC_BUCHI.tiff", 
               width = 20, height=16, res = 700, 
               compression = "lzw", units = "cm")
ggarrange(M5pred1,M5pred1s,M6pred1,M6pred1s,M7pred1,
          M7pred1s,M8pred1,M8pred1s,ncol=2,nrow=4)
dev.off()

tiff(file = "Figure6_MC_SCIO.tiff", 
               width = 20, height=16, res = 700, 
               compression = "lzw", units = "cm")
ggarrange(M1pred1,M1pred1s,M2pred1,M2pred1s,M3pred1,
          M3pred1s,M4pred1,M4pred1s,ncol=2,nrow=4)
dev.off()

```



